---
title: "Experiment 1C: Visual interference disrupts verbal cueing of visual recognition but not word repetition detection"
author: "Pierce Edmiston"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
---

We conducted Experiment 1C to rule out the possibility that visual interference disrupts task performance in general, regardless of the specificity of the visual interference effects. In this experiment we had participants perform a dual task. On some trials participants completed the same upright picture detection task as performed in Experiments 2A and 2B. On other trials  participants performed a word repetition task which does not require the visual knowledge. We expected visual interference to again disrupt the verbal cueing effect observed in Experiments 2A and 2B, but not to have an effect on word repetition detection.

```{r, echo = FALSE, message = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.path = "figs/",
  cache.path = ".cache/"
)

read_chunk("unilateral.R")
```

```{r, setup}
```

# Methods

## Participants

28 participants received course credit for participating in the experiment.

```{r}
unilateral %>%
  group_by(version) %>%
  summarize(N = length(unique(subj_id)))
```

```{r, subjs}
```

## Materials and Procedure

Experiment 2C was identical to Experiment 2A except that on a subset of trials
(25%) instead of two pictures a single word appeared, presented unilaterally. 
Which side the word appeared did not matter; participants
pressed the up arrow if the printed word was the same as the word they heard.
They pressed the down arrow if the printed word was not a repetition. Of
these word trials, 75% of the time the printed word was a repetition of
the auditory cue.

Participants were allowed to respond with any of the four arrow keys
on each trial. After initial data collection (N = 14), we revised the task
to disallow left or right responses on word repetition trials.

To allow for the additional word repetition task, we also excluded the 
baseline, noise cues that were presented in Experiments 2A and 2B.

# Results

```{r, overall-plot}
```

```{r, overall-error-plot}
```

## Effect of mask on cueing upright picture detection (replication)

In a replication of Experiments 2A and 2B, we observed a cueing effect on the
trials without any visual interfence, [stats]. Visual interference reduced
this cueing effect by X%, [stats].

```{r, pic-mod, echo = 1}
```

```{r, pic-error-mod, echo = 1}
```

## Effect of mask on word repetition

Visual interference did not have a detrimental effect on the speed, [stats], or
accuracy, [stats], at which repeated words were detected.

```{r, word-mod, echo = 1}
```

```{r, word-error-mod, echo = 1}
```

## Correlation between masking effects

The additional word repetition trials required participants to learn two sets
of response keys: left and right arrows for the upright picture detection trials,
and up and down arrows for the word repetition trials.

```{r, mask-correlation-plot}
```

```{r, mask-correlation-mod, echo = 1}
```

# Discussion
